\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[square,comma,numbers,sort&compress]{natbib}
\usepackage{bm}


\newcommand\ket [1] {|#1 \rangle }
\newcommand\bra [1] {\langle #1 |}
\newcommand{\bracket}[2]   {  \left<#1 |  #2\right>}
\newcommand{\av}[1]{\langle #1\rangle}
\newcommand{\bb}[1]{\mathbf{#1}}

% Short title
\shorttitle{Expenditure Motivation Blockchains}    

% Short author
\shortauthors{Waajacu}  

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}

\title[mode = title]{Expenditure Motivation Blockchains}

%\tnotemark[1,2]

%\tnotetext[1]{This document is the results of the research project
   % funded by the National Science Foundation.}

  %\tnotetext[2]{The second title footnote which is a longer text
    %matter to fill through the whole text width and overflow into
    %another line in the footnotes area of the first page.}

  \author[1]{Waajacu}[orcid=0000-0001-6386-9350]
  \cormark[1] 
  %\fnmark[1] 
  \ead{savethebeesandseeds@gmail.com} 
  \ead[url]{www.waajacu.com}

  %\credit{Conceptualization of this study, Methodology, Software}

  \address[1]{Santiago Restrepo Ruiz, Colombia.}

  \cortext[cor1]{Corresponding author} 
  %\cortext[cor2]{Principal corresponding author} 
  %\fntext[fn1]{This is the first author footnote. 
    %but is common to third author as well.}

  %\fntext[fn2]{Another author footnote, this is a very long footnote
    %and it should be a really long footnote. But this footnote is not
    %yet sufficiently long enough to make two lines of footnote text.}

  %\fntext[fn3]{K. Berry is the editor of \TeX Live.}

  %\nonumnote{This note has no numbers. I}

 \begin{abstract}
  Attention these tresure dynamics; 
  
  If one evil man knows to relate ides to a state of action; there be suffering, 
  
  how may I to use the method without sharing the method. 

  To relate expenditure to Honor, without reveling the formula to relate expenditure to Suffering. 

  To relate expenditure to the negative of Suffering, without allowing the sing in the formula to be flip. 

  Mathematics is a way of war and a way of peace, 

  The matematics of non evil. 

  Expenditure Motivation Features Of Capital, 
  
  Mechanisms of peacefull controlled unpressured path of rendition. 
  
  Optimization is shown benefits of a rendition by expending one's capital by maximizing 
  universal good concepts; this is the story of how 
  to secure the cryptografic fashion of one's conditions for rendition. 
  
  here is to conect language to mathematics.
  
  universal good concepts optimized, 
  
  those as universal hopefull starting, the value of determination and courage. 

  I can deer tell you, liberty was a mistake in latinoamerica ---it was implemented just as abandonment. 

  "Honor" has no market dumb me. !!

  change the "word" or change the idea.

  liberty is not those who owns the fault, 

  those who owns the fault are stupid people unchequed. 

  criptography as a driving force, weponaizable, 
  ---never to be serve to those who own the fault. 

  the world might get to be ok, 

  I need to find peace for my self...

  This is a secure encrypted signed protocol 
  to equilibrate Karma while avoiding War. 
  
\end{abstract}
 \begin{keywords}
  Honor, Maximum Knowledge Blockchain, Blockchain, Game Theory, Liberty & Surrendering Protocols. 
 \end{keywords}

 \maketitle
%\linenumbers

\section{Introduction}
Any good here to be understood, a monetary policy that enforces the Honor System. \\

Little can one construct with mathematics that produces not a weapon. 

Is a way of rendition, not a way to make money. 

Consider the scenario when liberty fails to sufficient interact to mitigate suffering 
in the world, liberty has failed to deliver basic happiness and spread wellbeeing. 
For a peaceful rendition of the powerful Expenditure Motivation Blockchains offer 
ways to give up power by maximizing one changes on the upcoming necessary system. \\

Is uderstood that or keep in mind that the desing of capital methods with only marginaly 
week parties deals unchequed control, --- 
liberty had no strengt to invervine where needed, they just pay to distribute the guilt. \\

Liberty is not to be lost... but stupid unchequed cocaine people rises to the top under liberty, 
and that brings suffering. 

Matematics can separate greed from power, ---to separate also power from individual choises, 
and can define hope and better future. ---Honor and determination as the thred that has power. 

The network algorithm asserts transparency and reflex by record the usage effort for the 
investors by a measure of Honor.


\section{Maximum Knowledge is Just Knowledge}
Not sure how to maximize knowledge, some derivation of Shannon or something, help is ok. 

\section{Mathematical Notation}

Honor variable H.
Honorary policy $\lambda$H.

Liberty variable L.
Libertarian policy $\lambda$L.

The people reclamation $\delta$. (that that honor could be tested for those who own nothing)

Maximum-Honor budget. 
Maximum-Liberty budget is a simple wallet of your own. 

Knowledge K.


\section{People live in the Dynamics}
When money is devalued then it's value drops; people live on absorving the degradation of the idea. 
At some high point the more you let your ownings fall the more you help; 
and people will bring on low the value on the reclamation of an Honor worthy policy, let matematics gide the way to a properous 
tomorrow ---keep your faith in science an let it guide out shared way, suspect widly of the stupidity, suspect also about 
the unadecuate tendency to behave by unaction in our Human capital. 

Look at me, knowing the anwser but knowing not the courange to bring it up behond a sheet of paper. 
Is of my science should must not be bought to make wepons, what if a prick decided to maximize suffering; 
what if a power drived by Honor shifted it ways thought the matematical centainty their efforts maximized suffering. 
This form of a matematics is a two side knife wepon; ---one could rule using these matematics but them will make it 
clear one is either maximising suffering or well beeing. 

Humans must reclaim order and happiness, we'll be better off thought the future if Honor is maximized; if Honor has learn the 
lesson of open science and broad education. Artistis have fail to make the world beautifull, us have fail to let 
Artistis achieve, the same as us have faild to let mathematicians speak; why is it so enfatic the power desire to fail their 
experiment on the world; or why is it you have sodimized my country with the lack of Hope. 

the reclamation of a space of time, for $\delta$ to reclaim a numeric control share of the flow of capital. 
$\delta$ is the people in the heart of those who should own the a share to serve the apparatus of any state, 
my science serves $\delta$ --- fools bring on pain with their governance, this is a fight to let mathematics rule. \\

$\delta_{\Delta}$ resist like friction the dynamics (velocity of money interchange) and generates and distributes 
well being among the poor, the alone and the forgotten majority. 

\section{Honor is higher than Liberty}

For the change is to measure honor by one's monetary actions, 
this is without centralized data, to make analytics of one's behavior. 

very complex, reduction abstraction is to name a variable Honor (H).


What is to have honor on the absence of data, 
Honor is to behold the strength of others 
Honor is to seek the highest purpose, 

for my sight sees liberty as the abandonment of the other, 

one can accumulate or give, but honor is in the purpose. 
so contracts establish the rate of growth and sets compromises that maximizes honor. 


for those alone, 
for those in need, 
for those without a change. 

No longer should such suffering be allowed, 

everything compromised is used to maximize one's Honor, 
everything one get to them self is a maximization of Liberty. 

So the rate of growth on a Honorary policy is to be higher than a liberty policy.


\section{Honor Contracts}
To state a compromise for one's capital. 
Dictionaries of interest, and maximization of private interests. 

\section{Criptographic Signatures}
sign to validate that the investment was delivery to maximize Honor.

\section{Liberty Penalties}
My eyes have seen, panic roots for liberty to avoid punishment. 
Fools think liberty is about driving fast cars while on cocaine. 

What is a Libertarian policy L, 

greed.

when liberty fails assert a contract that state left power from money surrender 
in a way that maximized their honor. 

Is a simple way to negotiate rendition and to maximal punctuation on 
the upcoming system, the honor system.

\section{Optimized derivatives}

\section{Access to reality}
Clean Energy Network, 

Clean energy has the highest honor along the energy methods. 

Energy is easy to implement for starting.

and how to access reality in a honor basis. 

\section{Protecting the Rich}
These royal bitches should own a face of shame, rather they live the face of fear and respond violently; so for us the way 
of fight is the way of a slow peace implementation of high advantage. This guarantees to protect the rich and works the way 
to reduce our shared guild on the accumulative suffering.

wisedom, wisedom! 

Fear be not dealed with force, that will increese the fear. 

Fear be addresed by matematical certainty and protocols. Here by a cryptographicaly secure rendition protocol. 
So Rich my give up the fight and allow the world a breath while asserting they caputal usage maximized their 
Honor by right of contribution. 

\section{Protecting the Poor}
Poor poor people every time it rains by night on the many days they get sick on these lands without care of shelters, 
mine of the lowest knew only violent rules without compassion. 
You won't believe me but one found ever too much often gifted white hair and deep powerful eyes on the street eating from trash cans.   
I've live up a third of the full extend of a century and cant give faith to have found a fiend on the eyes of a rich. 
And have many times found greatness on the eyes of a poor person. 
My vision is clear as the night sky, every more so often I see 
poverty trusts us a cradle for a good heart, 
so made this propositional weapon of a theoretical build for a system's science of hope. 

\section{Money Cycle of no-zsg Implementation}
On a no-zsg (no zero sum game) --- money can augment and money can decrees. On this environment no-one can 
accumulate capital to oppress her or his neighbor. You'll learn one day of the unnecessary suffering unlawfully people 
bring on the world with their armed resistance to change. 

\section{}
\section{}
\section{}

\section{Conclusions and outlook}

\begin{itemize}

\item
{\bf Exploring new platforms.}
The recent trend of studying FCIs in moir\'e materials has clearly demonstrated the intimate relation between FCI and material science. Searching for new solid-state platforms that can host FCIs will significantly stimulate further development of this field. The research in this direction will need contributions from material calculations via, for instance, density functional theory. In fact, progress is already being made in this direction. Going beyond graphene based materials, moir\'e systems built on transition metal dichalcogenides (TMD) are found to support topological flat bands~\cite{TMD_Wu2019,TMD_DasSarma2020,Li2021,TMD_Fu2021,TMD_Fu2021_2,TMD_DasSarma2021,TMD_Zhou2022}. Excitingly, a few numerical works have identified FCIs in twisted TMD homobilayers, like twisted bilayer ${\rm MoTe}_2$~\cite{TMDFCI_Li2021} and ${\rm WSe}_2$~\cite{FCITMD_Fu}. It requires more effort to thoroughly investigate FCI states and their competing phases in these new materials. These theoretical explorations will be greatly helpful to accelerate the experimental realization of zero-field FCIs.

\end{itemize}

\section{Acknowledgements}
Z. L. is supported by the National Key Research and Development Program of China through Grant No. 2020YFA0309200.

\bibliographystyle{is-unsrt}
\bibliography{mybibfile}

\end{document}