\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[square,comma,numbers,sort&compress]{natbib}
\usepackage{bm}


\newcommand\ket [1] {|#1 \rangle }
\newcommand\bra [1] {\langle #1 |}
\newcommand{\bracket}[2]   {  \left<#1 |  #2\right>}
\newcommand{\av}[1]{\langle #1\rangle}
\newcommand{\bb}[1]{\mathbf{#1}}

% Short title
\shorttitle{UPRIGHTNESS MATHEMATICS}    

% Short author
\shortauthors{\textit{Waajacu}}  

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}

\title[mode = title]{UPRIGHTNESS MATHEMATICS}

%\tnotemark[1,2]

%\tnotetext[1]{This document is the results of the research project
   % funded by the National Science Foundation.}

  %\tnotetext[2]{The second title footnote which is a longer text
    %matter to fill through the whole text width and overflow into
    %another line in the footnotes area of the first page.}

  \author[1]{\textit{Waajacu}}[orcid=0000-0001-6386-9350]
  \cormark[1] 
  %\fnmark[1] 
  \ead{savethebeesandseeds@gmail.com} 
  \ead[url]{www.waajacu.com}

  %\credit{Conceptualization of this study, Methodology, Software}

  \address[1]{Santiago Restrepo Ruiz, Colombia.}

  \cortext[cor1]{Corresponding author} 
  %\cortext[cor2]{Principal corresponding author} 
  %\fntext[fn1]{This is the first author footnote. 
    %but is common to third author as well.}

  %\fntext[fn2]{Another author footnote, this is a very long footnote
    %and it should be a really long footnote. But this footnote is not
    %yet sufficiently long enough to make two lines of footnote text.}

  %\fntext[fn3]{K. Berry is the editor of \TeX Live.}

  %\nonumnote{This note has no numbers. I}

 \begin{abstract}

  There is knowledge in the sape of the entropy function, leading a  
  
  base discovery for Mathematics; that takes away a recurrnet problem: 
  
  optimizing imprecise Hamiltonians leads surface paths that destroys Nature. \\

  Nature is too much of a Woman  for me, so let me gentil proceed with Data Hamiltonians. 

  An uprightness mathematics restrictcs and weaponize dynamics for the following procedure of description. 
  
  removing all damage it's revelations can produce, 

  meaning regular mathematics can be used to defeat or be used to defend, some how a transformation is in order that 
  makes it not posible to descrive damages to others. 

  Some restrictions are functional, some restrictions are in the base of mathematics it self... I was to lazy to study enough, 
  
  there are some things I cannot bring alone with a precise description, but there is a transfromation that 
  represents others in terms of one self and that knowledge proffs permit the undestinguisibility of one and the other. 

  so everything in the best intrest of one is the best intrest of all, 

  to plan you need data, to access the data one agrees to used but not be able to relate one self or those alike one self from 
  the others. So any usage of mathmatics to descruct is a lattent destruction of one self. 

  I'm trying to be very prcesise, these are not analigies. 

  Is a problem of ur languages that me and me alone cannot be precise about with a shorter text; ---the expression of 
  data sources that procet the others in the stored data so that it cannot be used to target an attack; 
  this will come latter, first Nature needs it's rescue ---later on, some generations from now 
  only expressibly method of law uncapable to distinguish one from the others in the base of it source; 
  there be no certaninty in the knowledge of "self" ---so any construction and destruct of the other cannot be 
  formulated, or known to hurt the other without certainty to hurt one self.

  crazy times, without guidance from our cultural heritage; 
  knowing and missing; missing most chances to do. 
  
  and 
  with thise ugly unlucky white basic cities an 
  unintended trap is left unattended, 
  there is no and was 
  
  that at the long run leads our sicence efforts weponazable against us all for the seek of the fiew. 
  
  the unwise strength to architect 
  
  ---working to ensure the Arabic gift of Mathematics serves no more the unholy persue for the destruction of Nature. 
  
  
  
  
  to translate the state of action, 
  
  encrypt the data, zero knowledge, 
  
  protect the people, zero knowledge only. 
  
  are my words suffering of alterations or beeing modified, fuck you any harmfull virus, let my science alone. 
  
  the dictionary of partisans biases. 
  
  
  Inflation will most lickly not let you build generational fortunes, 





  how may I to use the method without sharing the method. 

  To relate expenditure to Honor, without reveling the formula to relate expenditure to Suffering. 

  To relate expenditure to the negative of Suffering, without allowing the sing in the formula to be flip. 

  Mathematics is a way of war and a way of peace, 

  The mathematics of non evil. 

  Expenditure Motivation Features Of Capital, 
  
  Mechanisms of peaceful controlled unpressed path of rendition. 
  
  Optimization is shown benefits of a rendition by expending one's capital by maximizing 
  universal good concepts; this is the story of how 
  to secure the cryptography fashion of one's conditions for rendition. 
  
  here is to connect language to mathematics.
  
  universal good concepts optimized, 
  
  those as universal hopefully starting, the value of determination and courage. 

  I can deer tell you, liberty was a mistake in latinoamerica ---it was implemented just as abandonment. 

  "Honor" has no market dumb me. !!

  change the "word" or change the idea.

  liberty is not those who owns the fault, 

  those who owns the fault are stupid people unchecked. 

  cryptography as a driving force, weaponize, 
  ---never to be serve to those who own the fault. 

  the world might get to be ok, 

  I need to find peace for my self...

  This is a secure encrypted signed protocol 
  to equilibrium Karma while avoiding War. 
  
\end{abstract}
 \begin{keywords}
  Honor, Maximum Knowledge Blockchain, Blockchain, Game Theory, Liberty \& Surrendering Protocols. 
 \end{keywords}

 \maketitle
%\linenumbers

\section{Introduction}

\section{}
\section{}
\section{}

\section{Conclusions and outlook}

\section{Acknowledgments}

\bibliographystyle{is-unsrt}
\bibliography{mybibfile}

\end{document}