\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[square,comma,numbers,sort&compress]{natbib}
\usepackage{bm}


\newcommand\ket [1] {|#1 \rangle }
\newcommand\bra [1] {\langle #1 |}
\newcommand{\bracket}[2]   {  \left<#1 |  #2\right>}
\newcommand{\av}[1]{\langle #1\rangle}
\newcommand{\bb}[1]{\mathbf{#1}}

% Short title
\shorttitle{RENAMED COOPERATION OF RENDITION}    

% Short author
\shortauthors{\textit{Waajacu}}  

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}

\title[mode = title]{RENAMED COOPERATION OF RENDITION}

%\tnotemark[1,2]

%\tnotetext[1]{This document is the results of the research project
   % funded by the National Science Foundation.}

  %\tnotetext[2]{The second title footnote which is a longer text
    %matter to fill through the whole text width and overflow into
    %another line in the footnotes area of the first page.}

  \author[1]{\textit{Waajacu}}[orcid=0000-0001-6386-9350]
  \cormark[1] 
  %\fnmark[1] 
  \ead{savethebeesandseeds@gmail.com} 
  \ead[url]{www.waajacu.com}

  %\credit{Conceptualization of this study, Methodology, Software}

  \address[1]{Santiago Restrepo Ruiz, Colombia.}

  \cortext[cor1]{Corresponding author} 
  %\cortext[cor2]{Principal corresponding author} 
  %\fntext[fn1]{This is the first author footnote. 
    %but is common to third author as well.}

  %\fntext[fn2]{Another author footnote, this is a very long footnote
    %and it should be a really long footnote. But this footnote is not
    %yet sufficiently long enough to make two lines of footnote text.}

  %\fntext[fn3]{K. Berry is the editor of \TeX Live.}

  %\nonumnote{This note has no numbers. I}

 \begin{abstract}
  Extintion lyes mane ways. 

  uncontrolled war is one om them, must be prevented. 

  Negotiation is an art of peace, on this cryptography contructs the show for the way. 

  Two ginantic absolute commited parties figthing leads a dangeuos balance. 
  
  Coopeation mediated by criptograpy, a coordinated mutual rendition. 


\end{abstract}
 \begin{keywords}
  Honor, Maximum Knowledge Blockchain, Blockchain, Game Theory, Liberty \& Surrendering Protocols. 
 \end{keywords}

 \maketitle
%\linenumbers

\section{Introduction}
There were found not sufficient hearts to make the way be handed to the many. 

System stabilizes on two gigantic parties. 

These parties need to surrender the art of matematical negotiation of shared conflicts. 

Matematical guided cooperation. 

The shared expertice of survival. 

An antological drama are the habits in the Humans by the deficency of our languages. 

Except matematics!

To negotiate an agreed transfomation of the langauges must be accord. 

This is why is a work on progress, 

how do I free with language the language problem: that is not ortogonal to the scenes, sights and cosas. 

So with a gigantic matrix one can agree orthogonalize langauge, but many parties will not agree the same matrix. 

An elegant short entropy-like expression we can agree, but finish this must be. 

And is getting late, I might be going crazy searching a way alone, 

the academic process of a motivated youth leads science to wepons. 

solitude for me has save the world of all my mistakes, 

this old science of renamed cooperation of rendition owns a large effort of caution. 

caution is to assert methods can be used to negotiate not to destroy, 

parties interacts withtout sharing kwowledge 

parties to be mantain the strength of their maximas 

while the science of the caitous leads the way of a coordinated rendition. 

There be no more knoledge to be used in manipulation, 

There be no more a problem the unsyncronated expresions of languages. 


\section{}
begins by expresing the minimal required language to express that what is beeing negotiated and renditioned. 

And then someone smarter than me will lead the effor of optimizing the path in the action graph, and a better 
way than a graph. 

Enough be the self known inner strengh of reflexions to secure victory of porpouse, not victory of legacy. 

Legacy is a gift to the memory, porpouse is light for life. 

I fail the path of overcoming young knowing the way of a restrained unpleced life two has seen too much injustice. 

I'll be a voice if nothing else, 

the fury of my judgement lead me a way to finish pain without war, 

and you all to call me a losser when we are old enough, 

human history tells a very recent behaviour alike vengance to nature, 

with the same as always genosidal changes of rullers our efforts will not be ready coordinated, 

there be life for ever and there be light every where. 

here a steady solution for a dynamical expresion of gamifigiht one opimal and rewritable supreme policy 

of parties that game something they have noting to win directly on. 

The poblem was Pandora was to long of a book and simple man started to implement 

into the world with out finishing the book first, the panflate of all diciplines...
\section{}
\section{}

\section{Conclusions and outlook}

\section{Acknowledgments}

\bibliographystyle{is-unsrt}
\bibliography{mybibfile}

\end{document}